Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem

### 2018-02-22 paper.tex
didn't do that, instead refactored text now i will be doing that

\subsection{Typical GA Schema}
The basic iteration cycle of a genetic algorithm proceeds on a population
of individuals, each of which represents a search point in the space
of potential solutions of a given optimization problem.
In case of a canonical genetic algorithm, each individual is a binary vector
$ \vec{x} = ( x_1, x_2, \dots, x_n ) \in \{0, 1\}^n $
of fixed length $n$. The fitness function
$ f: \{0, 1\}^n \rightarrow \mathbb{R} $
provides a quality measure which is used by the selection procedure to direct
the search towards regions of the search space where the
average fitness of the population increases. The recombination operator
allows for the exchange of information between different individuals, and
mutation introduces innovation into the population.

After a uniform random initialization of the population
the evolution proceeds by iterating the steps selection,
recombination (crossover), and mutation (see figure~\ref{fig:ga})
until a termination criterion is fulfilled.
In most cases, the algorithm is terminated after a certain number of
iterations of the basic cycle or when a satisfactory fitness
level has been reached.

>>>>

\subsection{Typical GA Schema}
The basic iteration cycle of a genetic algorithm proceeds on a population
of individuals, each of which represents a search point in the space
of potential solutions of a given optimization problem.
In case of a canonical genetic algorithm, each individual is a binary vector
$ \vec{x} = ( x_1, \dots, x_n ) \in \{0, 1\}^n $
of fixed length $n$. The fitness function
$ f: \{0, 1\}^n \rightarrow \mathbb{R} $
provides a quality measure which is used by the selection procedure to direct
the search towards regions of the search space where the
average fitness of the population increases. The recombination operator
allows for the exchange of information between different individuals, and
mutation introduces innovation into the population. \\
This cycle is repeated until a termination criterion is fulfilled.
In most cases, the algorithm is terminated after a certain number of
iterations of the basic cycle or when a satisfactory fitness
level has been reached.
refer to figure~\ref{fig:ga} for a visual representation of this process.

The population size (denoted as $u$) depends on the nature of the problem,
but typically contains several hundreds or thousands of possible solutions.
Often, the initial population is generated randomly, allowing the entire range
of possible solutions (the search space).
Occasionally, the solutions may be `seeded' in areas where optimal solutions
are likely to be found.
